---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: '**Integrating objective measures of ADHD**'
author:
  - name: '**Deborah Apthorp**'
    affil: 1,2
    main: true
    orcid: '0000-0001-5785-024X'
    twitter: deborahapthorp
    email: dapthorp@une.edu.au
  - name: Katie Crocker
    affil: 1
    main: true
    email: 'kcrocke2@myune.edu.au'

affiliation:
  - num: 1
    address: School of Psychology, University of New England, NSW, Australia
  - num: 2
    address: School of Medicine and Psychology, Australian National University, ACT, Australia

main_findings:
  - "Online **behavioural measures** predict ADHD symptoms better than **eye movements**."
logoleft_name: images/betterhexlogo.png
logoright_name: images/UNE_logo.png
logocenter_name: images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

Diagnosis of Attention Deficit Hyperactivity Disorder (ADHD) is currently quite fragmented and ad hoc. Diagnostic criteria rely on either self-report, parent-report or both; the main validated survey for adults is the Adult ADHD Self-Report Scale (ASRS; REF). There is increasing interest in more objective measures to increase precision and reliability in diagnosis; since ADHD is construed as a disorder which affects attention, behavioural tasks which are designed to measure various aspects of attention should be applicable. In addition, eye tracking measures are a promising line of enquiry and have shown differences in lab-based studies between individuals with ADHD and controls [REF]. These have the potential to show early warning signs even in babies too young to perform behavioural tasks. We investigated the potential to use online webcam-based eye tracking and behavioural tasks for remote diagnosis. 

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Recruit online participants with and without diagnosed ADHD
2. Collect survey data (ASRS + demographics)
3. Online eye-tracking (RealEye)
4. Online behavioural data collection (Continuous Performance Task - Non-X)

# Methods

## Participants 

- 118 completed ASRS (Age: 18-60, M = 36; 24 male)
- 58 also completed eye tracking and CPT
- Dropout may have been caused by webcam and browser restrictions 

## Measures 

## Procedure



# Results

Here you may have some figures to show off: below I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r irisfigure, fig.cap='Here is a caption for the figure.', out.width="80%"}

plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")

```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# References
